---
title: "2: Dynamic Time Series"
subtitle: "Time Series and Panels"
author: "<large>J. Seawright</large>"
institute: "<small>Northwestern Political Science</small>" 
date: "`r format(Sys.Date(), '%A, %e %B, %Y')`"
output: 
  xaringan::moon_reader:
    css: 
      - "shinobi"
---
class: center, middle

```{r, load_refs, include=FALSE, cache=FALSE}
# Initializes the bibliography
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear", # Bibliography style
           max.names = 3, # Max author names displayed in bibliography
           sorting = "nyt", #Name, year, title sorting
           cite.style = "authoryear", # citation style
           style = "markdown",
           hyperlink = FALSE,
           dashed = FALSE)
#myBib <- ReadBib("assets/myBib.bib", check = FALSE)
# Note: don't forget to clear the knitr cache to account for changes in the
# bibliography.
library(DT)

ajgoogle <- read.csv("C:/Users/jnsno/OneDrive - Northwestern University/Seawright Teaching/TSCS Teaching/ajgoogle.csv")
```

---
class: center, middle

Here is a simple time-series model:

$$Y_{t} = \alpha + \beta X_{t} + \epsilon_{t}$$

---
class: center, middle

Suppose the error term has an $AR(1)$ process.

$$\epsilon_{t} = \rho \epsilon_{t-1} + \nu_{t}$$

---
class: center, middle

$$Y_{t} = \alpha + \beta X_{t} + \rho \epsilon_{t-1} + \nu_{t}$$

---
class: center, middle

$$\epsilon_{t-1} = Y_{t-1} - \alpha + \beta X_{t-1}$$

---
class: center, middle

$$Y_{t} = \alpha + \beta X_{t} + \rho (Y_{t-1} - \alpha + \beta X_{t-1}) + \nu_{t}$$
--

$$Y_{t} = (1 - \rho) \alpha + \rho Y_{t-1} + \beta X_{t} - \rho \beta X_{t-1} + \nu_{t}$$

---
class: center, middle

A more general time-series regression model:

$$Y_{t} = \alpha Y_{t-1} + \beta X_{t} + u_{t}$$

$$X_{t} = \rho X_{t-1} + e_{1,t}$$

$$u_{t} = \phi u_{t-1} + e_{2,t}$$
---
class: center, middle

Let's start simple: $\beta = \rho = \phi = 0$

--

$$Y_{t} = \alpha Y_{t-1} +  u_{t}$$

---
class: center, middle

Consider the following:

$$Y_{t} = \beta Y_{t-1} +  \epsilon_{t}$$

$$\epsilon_{t} = \rho \epsilon_{t-1} + \nu_{t}$$

---
#Assume
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
$$-1 < \beta < 1$$

$$-1 < \rho < 1$$

---

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

$$\rho Y_{t-1} = \rho \beta Y_{t-2} +  \rho \epsilon_{t-1}$$

$$\rho \epsilon_{t-1} = \rho Y_{t-1} - \rho \beta Y_{t-2}$$


---

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
$$Y_{t} = \beta Y_{t-1} +  \rho Y_{t-1} - \rho \beta Y_{t-2} + \nu_{t}$$

---
#The Workhorse Model

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

$$Y_{t} = \beta_{1} Y_{t-1} + \beta_{2} X_{t} +  \epsilon_{t}$$

$$\epsilon_{t} = \rho \epsilon_{t-1} + \nu_{t}$$

---
#The Workhorse Model

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

Keele and Kelly (2006) argue that the workhorse model should be estimated by OLS with a lagged dependent variable as long as:


- The dependent variable is **stationary.**
- The residuals are not strongly autocorrelated.

---
```{r, echo = TRUE}

for (i in 1:(nrow(ajgoogle)-1)) {
     ajgoogle$alexjoneslagged[i+1] <- ajgoogle$alexjones[i]
}

summary(lm(alexjones~alexjoneslagged, data=ajgoogle))
```

---
```{r, echo = TRUE}

for (i in 1:(nrow(ajgoogle)-2)) {
     ajgoogle$alexjoneslagged2[i+2] <- ajgoogle$alexjones[i]
}

summary(lm(alexjones~alexjoneslagged + alexjoneslagged2, data=ajgoogle))
```

---
```{r, echo = TRUE}

summary(lm(alexjones~alexjoneslagged + alexjoneslagged2 + donaldtrump + trumpapproval, data=ajgoogle))
```

---
```{r, echo = TRUE}

summary(lm(alexjones~alexjoneslagged + donaldtrump + trumpapproval, data=ajgoogle))
```

---
#Breusch-Godfrey Lagrange Multiplier Test

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

1. Estimate the model with OLS.
2. Regress residuals on the $X$ variables and lags of the residuals.
3. $(n-p) R^2$ converges to $\chi^{2}_{p}$.

---
```{r, echo = TRUE}

library(lmtest)

bgtest(alexjones~alexjoneslagged + alexjoneslagged2 + donaldtrump + trumpapproval, data=ajgoogle, order=12, type="Chisq", fill=NA)
```

---

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

No significant results on BG?

-- Just use OLS.


---

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

Significant results on BG but the model doesn't include a lagged DV?

-- Use Cochrane-Orcutt.

